The problem and promise of scale in multilayer networks

### 2020-01-23 paper/manuscript.Rmd
Update manuscript.Rmd

We generated seasonal multilayer social networks consisting of habitat-specific monolayers. Each layer was the social association network generated in one of three habitat types (lichen, open, and closed). Briefly, all GPS relocations were assigned to the corresponding habitat type and proximity-based social network layers were generated using the R package spatsoc (Robitaille et al. 2019) in *R version* (R CITATION).

We generated monolayer association networks for caribou for each habitat-by-season combination based on proximity of GPS fixes for individual caribou: we assumed association between two individuals if simultaneous GPS fixes (i.e., recorded within 5 minutes of each other) were within 50 m of one another (Lesmerises et al. 2018). In all networks, nodes represented individuals, intralayer edges represented associations between individuals in a given habitat type, and interlayer edges represented **XXXX [ALEC??]**.

We applied the ‘chain rule’, where each discrete spatiotemporal GPS fix was buffered by 50 m and we considered individuals in the same group if 50 m buffers for two or more individuals were contiguous, even if some individuals within the buffer were not within 50 m of one another. Group assignment based on the chain rule has commonly been applied to gregarious mammals, including caribou (Peignier et al. 2019; Lesmerises et al. 2018). We weighted edges of social networks by the strength of association between dyads of caribou using the simple ratio index (SRI, Cairns and Schwager 1987):

@@

where x is the number of fixes where individuals A and B were within 50 m of each other, y<sub>A</sub> is the number of fixes from individual A when individual B did not have a simultaneous fix, y<sub>B</sub> is the number of fixes from individual B when individual A did not have a simultaneous fix, and y<sub>AB</sub> is the number of simultaneous fixes from individuals A and B that were separated by >50 m (Farine & Whitehead 2015). Social groups were designated if two or more individuals occurred within 50 m of one another at any given time point. We generated social networks with the igraph package in R, version 1.2.2 (Csárdi & Nepusz 2006). For each multilayer network, we calculated XXX metrics (see below).

@@

As above, we generated social association networks in three habitat types and two seasons. For our baseline networks, we assumed individuals were in the same group if they were within a 50m spatial buffer of one another (see above). Based on visual (short distance) and auditory (long distnace) sensory modalities of caribou (REF?), we modified the spatial buffer and re-assigned groups at incremental distance between 5 and 500. Thus, at the finest social scale, only individuals within 5m of one another were considered in the same group, whereas at the coarset social scale, only individuals within 500m of one another were considered in the same group. Modifying social scale enabled us to assess the

@@

Studies of social network analysis vary in the number and frequency of observations as well as the data collection technique used to generate networks (Davis et al. 2018; Webber and Vander Wal 2019). Randomly select max number of observations - timegroups -  (right now 750). For each iteration, include n observations for each season for all individuals. Subsequent iterations include nstep more (right now 25), along with previously included to remove stochasticity. Parallels with observation data.

>>>>

We generated seasonal multilayer social networks consisting of habitat-specific monolayers. Each layer was the social association network generated in one of three habitat types (lichen, open, and closed). For habitat-specific networks, all GPS relocations were assigned to the corresponding habitat type and proximity-based social network layers were generated using the R package spatsoc (Robitaille et al. 2019) in *R version* (R CITATION).

Within each habitat-specific monolayer network, we assumed individuals were associating if simultaneous GPS fixes (i.e., recorded within 5 minutes of each other) were within a given distance of one another. Typically for ungulates and other gregarious mammals, the ‘chain rule’ is applied for group assignment. For GPS data, the chain rule is applied if discrete spatiotemporal GPS fixes buffered by a given distance formed a contiguous buffer for two or more individuals, even if some individuals within the buffer were not within the given distance of one another (Robitaille et al. 2019). Group assignment based on the chain rule has previously been applied to caribou at a distance of 50m (Peignier et al. 2019; Lesmerises et al. 2018). To assess the role of social scale in multilayer networks, we varied the threshold distance for group assignment between 5-500m (see *Social scale* section below). In all networks, nodes represented individuals, intralayer edges represented associations between individuals in a given habitat type, and interlayer edges represented **XXXX [ALEC??]**.

We weighted edges of social networks by the strength of association between caribou using the simple ratio index (SRI, Cairns and Schwager 1987):

@@

where x is the number of fixes where individuals A and B were within a given distance of each other, y<sub>A</sub> is the number of fixes from individual A when individual B did not have a simultaneous fix, y<sub>B</sub> is the number of fixes from individual B when individual A did not have a simultaneous fix, and y<sub>AB</sub> is the number of simultaneous fixes from individuals A and B that were separated by more than the given distance (Farine & Whitehead 2015). Social groups were designated if two or more individuals occurred within a given distance of one another at any given time point. For each multilayer network, we calculated XXX metrics (see below).

@@

We altered social scale based on visual (short distance) and auditory (long distnace) sensory modalities of caribou (REF?). Specifically, we modified the distance threshold required for group assignment (see above) and re-assigned groups at incremental distance between 5-500m. For example, at the finest social scale, only individuals within 5m of one another were considered in the same group, whereas at the coarset social scale, only individuals within 500m of one another were considered in the same group.

@@

Studies of social network analysis vary in the number and frequency of observations as well as the data collection technique used to generate networks (Davis et al. 2018; Webber and Vander Wal 2019).

Randomly select max number of observations - timegroups -  (right now 750). For each iteration, include n observations for each season for all individuals. Subsequent iterations include nstep more (right now 25), along with previously included to remove stochasticity. Parallels with observation data.
